---
title: "Incarceration Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("analysis.R")
```
## Introduction
- United States is the most incarcerated country in the world due to the significant
contribution of systemic racism. 
- For example, the prison system reveals to target
individuals of color through over-policing and the war on drugs, leading to the
disproportionate incarceration of people of color. 
- Through this report, I am examining the patterns of inequality
using the incarceration data collected by the [Vera Institute](https://github.com/vera-institute/incarceration-trends). I am
examining jail population rates by different races in different states, and
specfically Texas. 


### Summary
```{r, eval= FALSE}
summary_info
```
- In 2018, Colorado had the highest black to white jail ratio.
- In 2004, Texas had the highest rate of black people in jail. 
- In 2018,Georgia had the highest rate of Latin Americans in jail. 
- In 2018, Louisiana had the lowest rate of white people in jail.
- In 2018, Georgia had the highest rate of Asian Americans in jail. 


### Black Jail Population Rates Disproportionately Higher than White Rates
This scatter plot displays the white jail population rates on the y axis and the
black jail population rate on the x axis. This plot reveals how states have
disproportionate incarceration rates among black and white people. For example,
in Campbell County, Wyoming, there is a white jail population rate of 138.22, which
is significantly lower than their black jail population rate of 34883.72. 

```{r, echo=FALSE}
black_white_by_state
```


### 2018 Texas Map of Black/White Incarceration Ratios
This map displays the differences in black to white incarceration ratios
by counties in Texas of 2018. There are quite of lighter blue counties, which
have a higher black to white incarceration ratio. For example, Terrell County has
a black to white incarceration ratio of 41.99987. 

```{r, echo=FALSE}
blackwhite_ratio_map
```


### Terrell County, Texas Incarceration Rates by Race Since 1990
These plots show the comparison between incarceration rates of
white people and minorities in Terrell County, Texas since 1990. Black
and Latin Americans overall have about higher incarceration rates than White
Americans. These plots reveal how there can be such vast disparity in
incarceration rates between races in only one county. 
```{r, echo=FALSE}
latin_white
```



```{r, echo=FALSE, warning=FALSE, message=FALSE}
black_white
```