---
title: "Incarceration Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("anaylsis2.R")
```
## Introduction
- United States is the most incarcerated country in the world due to the significant
contribution of systemic racism. 
- For example, the prison system reveals to target
individuals of color through over-policing and the war on drugs, leading to the
disproportionate incarceration of people of color. 
- Through this report, I am examining the patterns of inequality
using the incarceration data collected by the [Vera Institute](https://github.com/vera-institute/incarceration-trends).

### Summary
```{r, eval= FALSE}
summary_info
```
- In 2018, Colorado had the highest black to white jail ratio.
- In 2004, Texas had the highest rate of black people in jail. 
- In 2018,Georgia had the highest rate of Latin Americans in jail. 
- In 2018, Louisiana had the lowest rate of white people in jail.
- In 2018, Georgia had the highest rate of Asian Americans in jail. 

### Trends Over Time Chart

### Black Jail Population Rates Disproportionately Higher than White Rates
This scatter plot displays the white jail population rates on the y axis and the
black jail population rate on the x axis. This plot reveals how states have
disproportionate incarceration rates among black and white people. For example,
in Campbell County, Wyoming, there is a white jail population rate of 138.22, which
is significantly lower than their black jail population rate of 34883.72. 

```{r, echo=FALSE}
black_white_by_state
```

### 2018 Texas Map of Black/White Incarceration Ratios
This map displays the differences in black to white incarceration ratios
by counties in Texas of 2018. There are quite of lighter blue counties, which
have a higher black to white incarceration ratio. For example, Terrell County has
a black to white incarceration ratio of 41.99987. 

```{r, echo=FALSE}
blackwhite_ratio_map
```

